% ============================================================
%  SCHOLA DOMESTICA — Level 1, Week 4, Lesson 17
%  Topic: Numbers 6–10 — Before, After, Between
%  10 problems | No speed drill
%  Compile with XeLaTeX
% ============================================================
\documentclass[12pt,letterpaper]{article}
\usepackage{sd_style}

\renewcommand{\lessonnum}{17}
\renewcommand{\lessonweek}{4}

\begin{document}

\lessonheader{4}{17}{Before, After, and Between — Numbers 6–10}

\begin{instructbox}
\noindent\textbf{\color{sd-blue}Instruction} \textit{(read aloud):}\\[4pt]
We already know before, after, and between for small numbers.
Now we use those words for numbers 6 through 10.
Use the number line below to help you.
\end{instructbox}

\vspace{6pt}
\begin{center}
\begin{tikzpicture}
  \draw[sd-blue, very thick, ->] (5.5,0) -- (11.3,0);
  \foreach \n in {6,...,10}{
    \draw[sd-blue, thick] (\n-0.5, -0.15) -- (\n-0.5, 0.15);
    \node[below] at (\n-0.5, -0.25) {\textbf{\n}};
  }
  \node[left] at (5.6,0) {\color{sd-blue}\textbf{$\cdots$}};
\end{tikzpicture}
\end{center}

\goldrule
\noindent\textbf{\color{sd-blue}Practice}
\vspace{6pt}

\prob What number comes \textbf{after} 7? \quad\ansblank

\vspace{8pt}
\prob What number comes \textbf{before} 9? \quad\ansblank

\vspace{8pt}
\prob What number is \textbf{between} 7 and 9? \quad\ansblank

\vspace{8pt}
\prob What number comes \textbf{after} 9? \quad\ansblank

\vspace{8pt}
\prob What number comes \textbf{before} 7? \quad\ansblank

\vspace{8pt}
\prob What number is \textbf{between} 6 and 8? \quad\ansblank

\vspace{8pt}
\prob Fill in all the blanks:\\[8pt]
\hspace{1cm}\ansblank, \textbf{7}, \ansblank\\[8pt]
\hspace{1cm}\ansblank, \textbf{9}, \ansblank\\[8pt]
\hspace{1cm}\ansblank, \textbf{10}, \ansblank \quad\textit{(Hint: what comes after 10?)}

\vspace{8pt}
\prob \textit{(Teacher reads)} Eight ducks swam in a line.
The duck in the middle swam between duck 7 and duck 9.
What number is the middle duck? \quad\ansblank

\vspace{8pt}
\prob Circle the number that is \textbf{between} 9 and 11:\\[6pt]
\hspace{2cm}{\Large 8 \quad 10 \quad 12}

\vspace{8pt}
\prob Write the numbers 6 through 10 in order, then circle the middle one:\\[6pt]
\hspace{1cm}\ansblank\quad\ansblank\quad\ansblank\quad\ansblank\quad\ansblank

\goldrule

\begin{checkbox}
\noindent\textbf{\color{sd-green}Knowledge Check}\\[4pt]
\setcounter{probnum}{0}
\prob What comes after 8? \quad\ansblank\\[8pt]
\prob What comes before 10? \quad\ansblank\\[8pt]
\prob What is between 6 and 8? \quad\ansblank
\end{checkbox}

\vfill
\noindent{\color{sd-blue}$\bigstar$ \textbf{Enrichment — Latin Numbers 6–10:}}\\[4pt]
\begin{tabular}{ccccc}
\textit{sex} & \textit{septem} & \textit{octō} & \textit{novem} & \textit{decem}\\
6 & 7 & 8 & 9 & 10
\end{tabular}\\[4pt]
Can you count to 10 in Latin from memory?
\textit{ūnus, duo, trēs, quattuor, quīnque, sex, septem, octō, novem, decem!}

\vspace{4pt}\hrule\vspace{3pt}
{\footnotesize\color{gray}\textit{Teacher note: "Before and after" on the number line directly prepares students
  for the concept of +1 and −1. If a student hesitates, have them physically
  point to the number on a printed number line.}}

\end{document}
